---
# ====================== SETUP SCRIPT: RUN THIS BEFORE RUNNING THE R SHINY APP ============================== #
---

It is very important that you run this script before running the Shiny Application. Make sure that you have downloaded the coNLL17-model from the GitHub repository and place the file in the same location as the Shiny Application script. 

Install and load necessary packages:
```{r}
install.packages("pacman")
library(pacman)
if(!require("devtools")) install.packages("devtools")
devtools::install_github("Guscode/Sentida") # Install Sentida
pacman::p_load(shiny,
               NLP,
               stats,
               graphics,
               stats,
               utils,
               tidytext,
               shinydashboard, 
               shinyBS,
               tm, 
               dplyr, 
               tidytext,
               plotly, 
               wordcloud2, 
               word2vec,
               ggplot2,
               highcharter,
               ape,
               shinyjs, 
               colourpicker,
               Sentida,
               shinycssloaders,
               shinybusy,
               shinyWidgets)
```

The coNLL17-model must be present within your R environment in order for the semantic similarity functionalities to work. Make sure that you have downloaded coNLL17-model from the GitHub repository and place it in the same location as the R Shiny Application Script.
```{r}
# Load the model
coNLL17_model <- read.word2vec(file = "coNLL17_model.bin", normalize = TRUE)
```

